### 2017-05-25 Paper/plos-latex-template/plos_latex_template.tex
today's edits

Drug discovery and the subsequent availability of new breakthrough therapeutics or `cures' are compelling examples of societal benefit from advances in research. Such advances are invariably collaborative, involving the contributions of many scientists building upon prior theory and experiment. Data mining of public and commercial data sources coupled with analysis of `cure networks' is a scalable digital methodology for assembling and analyzing the scientific history of these advances. The methodology for assembling is extensible beyond cure networks and such studies support (i) efficiency in  exploring  science history (ii) an improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research. In addition, they help make the scientific environment more citizen-accessible. Building upon techniques for single cure networks, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across these networks. We have enriched the content of these networks by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks for all five therapeutics and additional intersections in pairwise interactions between networks.

@@

\section*{Materials and Methods} 
% Place tables after the first paragraph in which they are cited.
A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1). Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors. 
 For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.\cite{bib1} but with specific modifications detailed below. An allowance of 2 months was made for `publication lag' when assembling referenced material. For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included. For each of the five therapeutics, a first-generation list of PubMed IDs (citing\_pmid) was harvested from the five different data sources (below).  
\begin{table}[!ht]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.9}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
\end{tabular}}
\vspace{2 mm}
\caption{
{\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies. The active ingredient for each of these five therapeutics is listed in column 1. While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic. The publication date for each patent is listed in the last column.}
%\begin{flushleft}  
%\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{table}

\textbf{Clinical trials} The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval. Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months period. PubMed was also searched with the unique identifier (NCT number) of any clinical trials that were identified to capture publications associated with the clinical trials that were not displayed in clinical trials.gov. To capture clinical trials publications that are not available in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as ``clinical trial'', and an appropriate date restriction as in searches of clinicaltrials.gov. For example, the search term (((``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields]) OR (``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields] OR ``campath"[All Fields])) AND (``1900/0101"[PDAT] : ``2001/07/31''[PDAT])) AND ``clinical trial"[Publication Type] was used to identify publications of clinical trials for Alemtuzumab.

@@

\textbf{Patents} For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand. Identification of this patent was performed using multiple web sources. The US patent number was then used to identify the patent and the non-patent citation list from Google Patents \cite{bib8} was manually processed by searching PubMed for appropriate pmids. While we developed a citation matching tool for non-patent literature for this purpose, the precision and recall rates from manual searches was far higher and were used to generate the data in this study.

@@

Citing\_pmids from the five different sources above  were combined and deduplicated. Using the Scopus database and its APIs, these citing\_pmids were mapped to ScopusIds (citing\_sid) and a second generation of cited references (cited\_sid) was extracted., These cited\_sids, were in turn, mapped back to pmids (cited\_pmid). Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_eid stage resulted in 1\% or less information loss, mapping at the cited\_eid to cited\_pmid resulted in 15-20 \% information loss. Accordingly the Scopus data  was used as the backbone of the publication component of the network and cited\_pmid was treated as an annotation layer.  These observations are summarized in Table 2 and include the count of null values when mapping from citing\_sid to cited\_sid.

\begin{table}[!ht]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.9}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & citing\_pmid count & citing\_eid count & cited\_eid count  & cited\_pmid count  \\ \hline
$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
\end{tabular}}
\vspace{2.5 mm}
\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies. A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature. Citing\_pmids were mapped to Scopus identifiers (citing\_eid), which were used, in turn, to retrieve literature cited by this foundational set (cited\_eid). Cited\_eids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field} 
\label{table2}
%\end{adjustwidth}
\end{table}

@@

We also calculated the RBR metric of Williams et al. (\textit{ibid}) with some modifications. The RBR metric is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed. A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken. Therefore, we created two new variants of the RBR; network RBR (nRBR) and document-based RBR (dRBR). nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background. Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.

@@

% Place figure captions after the first paragraph in which they are cited.
\begin{figure}[!h]
\caption{{\bf Bold the figure title.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

% Results and Discussion can be combined.
\section*{Results and Discussion}
\subsection*{Network Features}
\subsection*{Intersection Across Networks} this is a 
\subsection*{Supporting awards and peer-review}
\subsection*{Future Directions}

\begin{table}[!ht]
%\begin{adjustwidth}{-0.51in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\vspace{2.5 mm}
\scalebox{0.8}{
\begin{tabular}{|l| l| l| l| l| l| l| l|}
\hline
alem(A) & imat(I) & nela(N) & ramu(R) & suni(S) & combination  & intersection\_count &no\_of\_drugs\\ 
 \hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
X & X & X & X & X & AINRS &  \textbf{14} & 5 \\ 
\hline
X & X &  & X & X & AIRS & \textbf{107} & 4 \\ 
\hline
X & X & X & X &  & AINR &  28 & 4 \\ 
\hline
X & X & X &  & X & AINS &  25 & 4 \\ 
\hline
& X & X & X & X & INRS &  22 & 4 \\ 
\hline
X &  & X & X & X & ANRS &  16 & 4 \\ 
\hline 
& X &  & X & X & IRS & \textbf{1762} & 3 \\ 
\hline
X & X &  & X &  & AIR & 231 & 3 \\ 
\hline
X & X &  &  & X & AIS & 211 & 3 \\ 
\hline
X &  &  & X & X & ARS & 156 & 3 \\ 
\hline
X & X & X &  &  & AIN &  81 & 3 \\ 
\hline
X &  & X & X &  & ANR &  56 & 3 \\ 
\hline 
& X & X &  & X & INS &  49 & 3 \\ 
\hline
& X & X & X &  & INR &  44 & 3 \\ 
\hline
 &  & X & X & X & NRS &  40 & 3 \\ 
\hline
X &  & X &  & X & ANS &  32 & 3 \\ 
\hline 
&  &  & X & X & RS & \textbf{7442} & 2 \\ 
\hline
& X &  &  & X & IS & 5415 & 2 \\ 
\hline
& X &  & X &  & IR & 2507 & 2 \\ 
\hline
X & X &  &  &  & AI & 1240 & 2 \\ 
\hline
X &  &  & X &  & AR & 448 & 2 \\ 
\hline
X &  &  &  & X & AS & 359 & 2 \\ 
\hline
X &  & X &  &  & AN & 334 & 2 \\ 
\hline 
& X & X &  &  & IN & 232 & 2 \\ 
\hline
&  & X & X &  & NR & 115 & 2 \\ 
\hline 
 &  & X &  & X & NS & 111 & 2 \\ 
\hline
&  &  & X &  & R & \textbf{49006} & 1 \\ 
\hline 
&  &  &  & X & S & 34257 & 1 \\ 
\hline 
& X &  &  &  & I & 27706 & 1 \\ 
\hline
X &  &  &  &  & A & 8978 & 1 \\ 
\hline
&  & X &  &  & N & 2498 & 1 \\ 
\hline
\end{tabular}}
\vspace{2.5 mm}
\caption{
{\bf Intersecting Publications Across Networks} Intersections were calculated for the set of publications associated with each network. Both citing and cited references were included in each set and  Scopus identifiers were used to to minimize information loss (Table 2). Intersection counts are shown for all possible combinations of the five therapeutics. The largest intersection count in each combination group is shown in boldface. Therapeutic names are abbreviated as follows: Alemtuzumab as alem(A), Imatinib as imat(I), Nelarabine as nela(N), Ramucirumab as ramu(R), and Sunitinib as suni(S). }

@@

No idea what to say...

@@

\section*{Discussion}

Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero~\cite{bib3}.

@@

>>>>

Drug discovery and the subsequent availability of new breakthrough therapeutics or `cures' are compelling examples of societal benefit from advances in research. Such advances are invariably collaborative, involving the contributions of many scientists in a `cure network' where prior theory and experiment is built upon. Data mining of public and commercial data sources coupled with network analysis is a scalable digital methodology for assembling and analyzing the history of scientific advances. This methodology is extensible beyond cure networks and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research. Building upon prior techniques for single cure networks and linking the work of approximately 200,000 authors in 100,000 scientific publications, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across networks. We have enriched the content of these five networks by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as a core set of awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented by these networks.

@@

\section*{Materials and Methods} 
% Place tables after the first paragraph in which they are cited.
A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1). Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors. 
 For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.\cite{bib1} but with specific modifications detailed below. An allowance of 2 months was made for `publication lag' when assembling referenced material. For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included. For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (below).  
\begin{table}[!ht]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.9}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
\end{tabular}}
\vspace{2 mm}
\caption{
{\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies. The active ingredient for each of these five therapeutics is listed in column 1. While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic. The publication date for each patent is listed in the last column.}
%\begin{flushleft}  
%\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{table}

\textbf{Clinical trials} The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval. Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months. To capture publications associated with the clinical trials that were not displayed in clinical trials.gov, PubMed was also searched with the unique identifier (NCT number) of any clinical trials that were identified. To capture publications of clinical trials not registered in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as ``clinical trial'', and an appropriate date restriction as in searches of clinicaltrials.gov. For example, the search term (((``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields]) OR (``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields] OR ``campath"[All Fields])) AND (``1900/0101"[PDAT] : ``2001/07/31''[PDAT])) AND ``clinical trial"[Publication Type] was used to identify publications of clinical trials for Alemtuzumab.

@@

\textbf{Patents} For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand. Identification of this patent was performed using multiple web sources. The US patent number was then used to identify the patent and the non-patent citation list from Google Patents \cite{bib8} was manually processed by searching PubMed for appropriate pmids. While we developed a citation matching tool for non-patent literature for this purpose, the accuracy of manual searches was far higher and were used to generate the data in this study.

@@

Citing\_pmids from the five different sources above  were combined and deduplicated. Using the Scopus database and its APIs, these citing\_pmids were mapped to Scopus identifiers (citing\_sid) from which a second generation of cited references (cited\_sid) was extracted., These cited\_sids, were in turn, mapped back to pmids (cited\_pmid). Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_sid stage resulted in 1\% or less information loss, mapping at the cited\_sid to cited\_pmid resulted in 15-20 \% information loss. Accordingly the Scopus data  was used as the backbone of the publication component of the network and the cited\_pmid information was treated as an annotation layer.  These observations are summarized in Table 2 and include the count of null values when mapping from citing\_sid to cited\_sid.

@@

We also calculated the RBR metric of Williams et al. (\textit{ibid}) with some modifications. The RBR metric is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed. A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken. Therefore, we created two new variants of the RBR; network RBR (nRBR) and document-based RBR (dRBR). nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background. Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.\\
\vspace{2.5 mm}

\textbf{Notation and Calculations}
\begin {itemize}
\item $d_i =$  therapeutic, e.g., alemtuzumab(alem) or imatinib(imat)
\item $N_i =$ the network of a therapeutic $d_i$;
\item $\mathcal{N}$ = union of all networks $N_i$
\item $\mathcal{G}$ the global network - the set of all authors and publications in $\mathcal{N}$ 
\item $\mathcal{M}$ the set of all subnetworks - ie $\{N_1,N_2,N_3,N_4,N_5\}$
\item $c_n(\mathfrak{p})$ citation of a publication $\mathfrak{p}$ in a network $n$
\item $\mathcal{C}_\mathfrak{p}^n$ =the set of publications which cites $\mathfrak{p}$ in a network $n$
\item $wc_n(\mathfrak{p})$  weighted citation of a publication $\mathfrak{p}$ in a network $n$
\item $\mathcal{A}_\mathfrak{a}^n$ the set of publications for an author $\mathfrak{a}$ in a network $n$
\item $pir_n(\mathfrak{a})$ the PIR  score of an author in a Network $n$ in $\mathcal{M}$
\item $npir(\mathfrak{a})$ the PIR score of an author  $\mathfrak{a}$ in the Network  $\mathcal{N}$ 
\item $ir(\mathfrak{a})$ partitioning of a research metric for an author $\mathfrak{a}$ 
\item $ic_{d_i}(\mathfrak{a})$ = total \# in-degree count for an author $\mathfrak{a}$  for drug $d_i$. (ie. = $\|\mathcal{A}_\mathfrak{a}^{d_i}\|$)
\item $ic_n(\mathfrak{a})$ = total \# in-degree count for an author $\mathfrak{a}$  in  $\mathcal{N}$ (i.e = $\|\mathcal{A}_\mathfrak{a}^{N}\|$)
\item $ nrbr_{d_i}(\mathfrak{a}) $ modified RBR score normalized to its network $\mathcal{N}$ for a drug $d_i$
\item $ grbr_{d_i}(\mathfrak{a}) $ modified RBR score normalized to the global network $\mathcal{G}$  for a drug $d_i$
\end{itemize}

\textbf{PIR Score}: We define the global network $\mathcal{N}$ as the union of the each individual sub-network of a therapeutic $d_i$. In other words 
$$ \mathcal{N} = \cup_{i =1}^{5} \mathcal{N}_i $$
Let $c_n(\mathfrak{p})$ be the citation score of the the paper $\mathfrak{p}$ in a network $n$, and $\mathcal{C}_\mathfrak{p}^n$ be the set of publication which cites $\mathfrak{p}$. Then we define the weighted citation of a paper $\mathfrak{p}$ as $$wc_n(\mathfrak{p}) = c_n(\mathfrak{p}) + \sum_{g\in \mathcal{C}_\mathfrak{p}^n}  c_n(g) $$
Let $\mathcal{A}_a^n$ be the set of publications for an author $\mathfrak{a}$ in a Network $n$. Then the PIR score  for an author $\mathfrak{a}$  in network $n$ is defined as $$ pir_n(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^n}  wc_n(\mathfrak{p}) $$

More simply, the PIR score for an author  $\mathfrak{a}$ in a Network $n$ is  $$ pir_n(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^n } \big[c_n(p) + \sum_{g\in \mathcal{C}_\mathfrak{p}^n}  c_n(g)\big] $$

Next we define the nPIR score $npir(\mathfrak{a})$, which is $pir$ score based on the  total network $\mathcal{N}$. For convenience, instead of denoting it $pir_N$, we use $npir$   Furthermore  we define the isolation of  research  metric $ir(\mathfrak{a}):\mathcal{R}\rightarrow [1,\infty]$  of an author $\mathfrak{a}$ as 
$$ir(\mathfrak{a})= \dfrac{ npir({\mathfrak{a}})} {\sum_{1}^{5} pir_{d_i}(\mathfrak{a})} $$
where $\mathcal{R}$ is the set of all authors in $\mathcal{N}$  and  $pir_{d_i}(\mathfrak{a})$ is the PIR score of the author $\mathfrak{a}$ restricted to only drug network $\mathcal{D}_i$ . If $ir(\mathfrak{a})$ approaches 1, the author's $\mathfrak{a}$ contribution to each drug is partitioned. The greater the $ir$, the closer  the interaction of the author's papers between the networks.

\textbf{RBR Score}:
\begin{itemize}
\item nRBR or network RBR is the ratio of an authors' count of publications in a network to the total number of the publications in the global Network. 
Lets define in-degree count $ic_{d_i}(\mathfrak{a})$ of an author $\mathfrak{a}$ as the total number of the publication which is in the network $\mathcal{N}_i$ of the drug $d_i$, similarly lets $ic_{n}$ be the number of the paper that author $\mathfrak{a}$ published in the total Network(5-drug's network) $\mathcal{N}$. Then we define, nRBR of an author $\mathfrak{a}$  for a drug $d_i$ as follow.
$$ nrbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{N}(\mathfrak{a})}$$
\item gRBR or global RBR is the ratio of an author's count of publications in a network to the author's total publication count. $\mathcal{G}$. Thus, $grbr$ score of an author  $\mathfrak{a}$  for the drug $d_i$ is defined as 
$$grbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{G}(\mathfrak{a})}$$
where $ic_{G}$ is the total number of publication that an author $\mathfrak{a}$ currently has.
\end{itemize}

@@

% Place figure captions after the first paragraph in which they are cited.

% Results and Discussion can be combined.
\section*{Results and Discussion}

Scientific publications form the backbone of each of these five networks. The initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential. Accordingly. we explored the extent and nature of intersections across networks, we calculated intersection counts for all possible combinations of Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib (Table 3). 14 publications are cited in all five networks and are shown in Table 4.

\begin{table}[!ht]
\begin{adjustwidth}{-1.0in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.8}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
\hline
SourceYear & SourceName & Author(s) \\ 
  \hline
1958 & J. Am. Stat. Assoc. & Kaplan E.R., Meier P. \\ 
1963 & Science & Jerne, N. K. and Nordin, A. A.  \\ 
1972 & J R Stat Soc & Cox DR.  \\ 
1976 & Anal. Biochem. & Bradford MM \\ 
1977 & Br J Cancer & R. Peto, M.C. Pike, and P. Armitage  \\ 
1977 & Proc. Natl. Acad. Sci. & Sanger, F., S. Nicklen, and A.R. Coulson.  \\ 
1983 & J Immunol Methods & Mosmann T  \\ 
1984 & Adv Enzyme Regul & T.C. Chou, and P. Talalay  \\ 
1989 & Molecular Cloning: A Laboratory Manual & Sambrook, J., Fritsch, E. and Maniatis, T.  \\ 
1994 & Acta Crystallogr D & Collaborative Computational Project 4 \\ 
1994 & Acta Crystallogr. A & Navaza J.  \\ 
1997 & Cell & Levine, A. J. \\ 
1997 & Am. J. Pathol. & Perez-Atayde, A. R., Sallan, S. E., Tedrow, U., Connors, S., Allred, E., and Folkman, J.  \\ 
1998 & CA: A Cancer Journal for Clinicians & SH Landis T Murray S Bolden PA Wingo \\ 
\hline
\end{tabular}}
\vspace{2.5 mm}
\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies. A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature. Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve literature cited by this foundational set (cited\_sid). Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field} 
\label{table4}
\end{adjustwidth}
\end{table}

Thus, we also applied intersection analysis as above at a finer level of granularity by computing intersection counts for first generation citations (citing\_pmid) and second generation citations (cited\_sid). The results are displayed as Venn diagrams in Figures 1 and 2 respectively. Strikingly, no publications are common to all five networks at the first generation level although a single publication, the highly influential work of Kohler and Milstein\cite{bibKohler}, is cited in four out of five networks. All 14 publications cited in our set of five networks were in the second generation of citations and another 198 were found  across various the four-network combinations, roughly an order of magnitude greater than the case of cited references.  We manually grouped the 14 publications using high level descriptive terms and noted statistical techniques (5 publications), molecular and cell biological methods (4), analytical and structural biochemistry techniques (3) and cancer biology (2). Of these last two, one is a review of the p53 gene [cite] and the second is a study of angiogenesis in children with acute lymphoblastic leukemia [cite]. Thus, the majority of this small set of 14 publications concerns methods that are heavily cited in these therapeutic development networks. We are actively working on characterizing the entire dataset as well as intersecting subsets using methods that would scale to thousands of publications and these results will be shared in another publication [needs to be reworded].

\begin{table}[!ht]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.9}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
\end{tabular}
}
\vspace{2.5 mm}
\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies. A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature. Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid). Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field} 
\label{table2}
%\end{adjustwidth}
\end{table}

\begin{figure}[!h]
\centering
\includegraphics[scale=0.15]{citing_pmid.png}
\caption{{\bf Publications Common To First Generation References in Networks}
Intersections were calculated across all five networks for citing\_pmids (the first generation of references) as well as cited\_sids (the second generation of references) and displayed as a Venn diagram.
No publications are common to all five networks. A single publication is cited in four of five networks. Abbreviations: alem (Alemtuzumab),imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig1}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[scale=0.15]{cited_sid.png}
\caption{{\bf Publications Common To Second Generation References in Networks}
Intersections were calculated across all five networks for cited\_sids (the first generation of references) as well as cited\_sids (the second generation of references) and displayed as a Venn diagram.
14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
\end{figure}

\subsection*{Network Features}
\subsection*{Intersection Across Networks} this is a 
\subsection*{Supporting awards and peer-review}
\subsection*{Future Directions}

\begin{table}[!ht]
%\begin{adjustwidth}{-0.51in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\vspace{2.5 mm}
\scalebox{0.8}{
\begin{tabular}{|l| l| l| l| l| l| l| l|}
\hline
alem(A) & imat(I) & nela(N) & ramu(R) & suni(S) & combination  & intersection\_count &no\_of\_drugs\\ 
 \hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
X & X & X & X & X & AINRS &  \textbf{14} & 5 \\ 
\hline
X & X &  & X & X & AIRS & \textbf{107} & 4 \\ 
\hline
X & X & X & X &  & AINR &  28 & 4 \\ 
\hline
X & X & X &  & X & AINS &  25 & 4 \\ 
\hline
& X & X & X & X & INRS &  22 & 4 \\ 
\hline
X &  & X & X & X & ANRS &  16 & 4 \\ 
\hline 
& X &  & X & X & IRS & \textbf{1762} & 3 \\ 
\hline
X & X &  & X &  & AIR & 231 & 3 \\ 
\hline
X & X &  &  & X & AIS & 211 & 3 \\ 
\hline
X &  &  & X & X & ARS & 156 & 3 \\ 
\hline
X & X & X &  &  & AIN &  81 & 3 \\ 
\hline
X &  & X & X &  & ANR &  56 & 3 \\ 
\hline 
& X & X &  & X & INS &  49 & 3 \\ 
\hline
& X & X & X &  & INR &  44 & 3 \\ 
\hline
 &  & X & X & X & NRS &  40 & 3 \\ 
\hline
X &  & X &  & X & ANS &  32 & 3 \\ 
\hline 
&  &  & X & X & RS & \textbf{7442} & 2 \\ 
\hline
& X &  &  & X & IS & 5415 & 2 \\ 
\hline
& X &  & X &  & IR & 2507 & 2 \\ 
\hline
X & X &  &  &  & AI & 1240 & 2 \\ 
\hline
X &  &  & X &  & AR & 448 & 2 \\ 
\hline
X &  &  &  & X & AS & 359 & 2 \\ 
\hline
X &  & X &  &  & AN & 334 & 2 \\ 
\hline 
& X & X &  &  & IN & 232 & 2 \\ 
\hline
&  & X & X &  & NR & 115 & 2 \\ 
\hline 
 &  & X &  & X & NS & 111 & 2 \\ 
\hline
&  &  & X &  & R & \textbf{49006} & 1 \\ 
\hline 
&  &  &  & X & S & 34257 & 1 \\ 
\hline 
& X &  &  &  & I & 27706 & 1 \\ 
\hline
X &  &  &  &  & A & 8978 & 1 \\ 
\hline
&  & X &  &  & N & 2498 & 1 \\ 
\hline
\end{tabular}}
\vspace{2.5 mm}
\caption{
{\bf Intersecting Publications Across Networks} Intersections were calculated for the set of publications associated with each network. Both citing and cited references were included in each set and  Scopus identifiers were used to to minimize information loss (Table 2). Intersection counts are shown for all possible combinations of the five therapeutics. The largest intersection count in each combination group is shown in boldface. Therapeutic names are abbreviated as follows: alem (Alemtuzumab), imat(Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni (Sunitinib). }

@@

@@

%\section*{Discussion}

@@

\begin{figure}[!h]
\caption{{\bf Bold the figure title.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\includegraphics{citing_pmid.png}
\label{fig2}
\end{figure}
